### 2022-05-31 main/chapter_2ljets.tex
add low region def table
add low region defn table
add preselection table
add list of disco regions
fix quotes
reduce gev noise

\clearpage
\subsection{Cheat-sheet}
Uncomfortably many event variables are used to define the regions of this
analysis.
To aid future revision of their meanings, definitions, and references for these
variables are collected here.
\begin{itemize}
\item $\met$: missing transverse momentum
\item $\metsig$: object-based missing transverse momentum significance;\\
described in Section~\ref{sec:2ljets_metsig}
\item $\ptjone$: transverse momentum of the hardest jet%
\vspace{0.5em}
\item $\mll$: invariant mass of the hardest two leptons
\item $\mjj$: invariant mass of the two hardest jets
\item $\mbb$: invariant mass of the two hardest b-tagged jets
\item $\mjetone$: mass of the hardest jet
\item $\mttwoll$: `stransverse` mass of the lepton pair with massless invisibles;\\
described in Section~\ref{sec:2ljets_mt2}
\vspace{0.5em}
\item $\rll$: distance in $\eta\textrm{--}\phi$ between the lepton pair
\item $\rjj$: distance in $\eta\textrm{--}\phi$ between the two hardest jets%
\vspace{0.5em}
\item $\njet$: number of signal jets
\item $\nbtag$: number of b-tagged jets;
described in Section~\ref{sec:2ljets_btagging}
\vspace{0.5em}
\item $\dphillmet$: azimuthal angle between the lepton pair and $\ptmiss$
\item $\dphijmet$: azimuthal angle between the hardest jet and $\ptmiss$
\end{itemize}
All of these are physical properties of particles or collections of particles.
Please remember that none is an exact or true value;
all are estimates based on approximate reconstructions.
While this distinction is easy to drop in lax language, it is necessary to
understand the shapes of noisy variables such as $\mjj$ and indeed the
existence of $\metsig$.

@@

\TODO{define presel, preselection SFOS 25 1j met>100 metsig>6}

@@

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lcccccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X/\eV[G]$
& $\Delta R_X$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj \in 60\textrm{--}110$
&
$\rjj \in 0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\quad VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\heartsuit \mjj \in 20\textrm{--}60 \mid 60\textrm{--}110$
& $\rjj < 1.6$
\\[.5em]
\quad VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\heartsuit \mjj > 20$
& $\heartsuit \rjj > 1.6$
\\[1em]
SR-High-1J
&
$\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone \in 60\textrm{--}110$
&
\\[.5em]
\quad VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\heartsuit \mjetone \in 20\textrm{--}60 \mid 60\textrm{--}110$
&
\\[1em]
SR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb \in 60\textrm{--}150$
&
\\[.5em]
\quad VR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $\heartsuit 12\textrm{--}18$
& $\mbb \in 60\textrm{--}150$
&
\end{tabular}
\small
\\[1em]
Common: presel, $\mll \in 71\textrm{--}111\,\eV[G]$, $\mttwo > 80\,\eV[G]$
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are marked $\heartsuit$.
\TODO{}
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lcccccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X/\eV[G]$
& $\ptjone/\eV[G]$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $\mjj \in 60\textrm{--}110$
& $> 60$
\\[.5em]
\quad VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\mjj \in 60\textrm{--}110$
& $\heartsuit < 60$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\heartsuit \mjj \in 20\textrm{--}60 \mid 60\textrm{--}110$
& $\heartsuit $
\\[.5em]
CR-tt
& $\geq 2$
& $\heartsuit \geq 1$
& $\heartsuit 9\textrm{--}12$
& $\heartsuit \mjj > 20$
& $> 60$
\end{tabular}
\small
\\[0.5em]
Common: presel, $\mll \in 81\textrm{--}101\,\eV[G]$, $\mttwo > 80\,\eV[G]$
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are marked $\heartsuit$.
\TODO{}
}
\label{tab:2ljets_int}
\end{table}

@@

@@

@@

>>>>

\clearpage
\subsection{Cheat-sheet}
Uncomfortably many event variables are used to define the regions of this
analysis.
To aid future revision of their meanings, definitions, and references for these
variables are collected here.
All units are $\eV[G]$ where appropriate.
\begin{itemize}
\item $\met$: missing transverse momentum
\item $\metsig$: object-based missing transverse momentum significance;\\
described in Section~\ref{sec:2ljets_metsig}
\item $\ptjone$: transverse momentum of the hardest jet%
\vspace{0.5em}
\item $\mll$: invariant mass of the hardest two leptons
\item $\mjj$: invariant mass of the two hardest jets
\item $\mbb$: invariant mass of the two hardest $b$-tagged jets
\item $\mjetone$: mass of the hardest jet
\item $\mttwoll$: `stransverse' mass of the lepton pair with massless invisibles;\\
described in Section~\ref{sec:2ljets_mt2}
\vspace{0.5em}
\item $\rll$: distance in $\eta\textrm{--}\phi$ between the lepton pair
\item $\rjj$: distance in $\eta\textrm{--}\phi$ between the two hardest jets%
\vspace{0.5em}
\item $\njet$: number of signal jets
\item $\nbtag$: number of b-tagged jets;
described in Section~\ref{sec:2ljets_btagging}
\vspace{0.5em}
\item $\dphillmet$: azimuthal angle between the lepton pair and $\ptmiss$
\item $\dphijmet$: azimuthal angle between the hardest jet and $\ptmiss$
\end{itemize}
All of these are physical properties of particles or collections of particles.
Please remember that none is an exact or true value;
all are estimates based on approximate reconstructions.
While this distinction is easy to drop in lax language, it is necessary to
understand the shapes of noisy variables such as $\mjj$ and indeed the
existence of $\metsig$.

@@

Table~\ref{tab:2ljets_presel}
\TODO{define presel, preselection SFOS 25 1j met>100 metsig>6}

@@

\begin{table}[tp]
\centering
\begin{tabular}{c}
Preselection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[.5em]
$\njet \geq 1$
\\[.5em]
same flavour, opposite charge $\ell^+\ell^-$
\\[.5em]
$p_\mathrm{T}^{\,\ell_2} > 25\,\eV[G]$
\\[.5em]
$\met > 100\,\eV[G]$
\\[.5em]
$\metsig > 6$
\end{tabular}
\caption{%
``Preselection'': requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\quad VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[.5em]
\quad VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[.5em]
\quad VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[.5em]
\quad VR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\small
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111\,\eV[G]$,
$\mttwo > 80\,\eV[G]$.
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are \uwave{underlined}.
\TODO{caption}
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $\mjj$
& $\ptjone$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $60\textrm{--}110$
& $> 60$
\\[.5em]
\quad VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $60\textrm{--}110$
& $\uwave{< 60}$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $\uwave{\hphantom{< 60}}$
\\[.5em]
CR-tt
& $\geq 2$
& $\uwave{\geq 1}$
& $\uwave{9\textrm{--}12}$
& $\uwave{20}$
& $> 60$
\end{tabular}
\small
\\[1em]
Common: Preselection,
$\njet \geq 2$,
$\mll \in 81\textrm{--}101\,\eV[G]$,
$\mttwo > 80\,\eV[G]$.
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are \uwave{underlined}.
\TODO{caption}
}
\label{tab:2ljets_int}
\end{table}

@@

Table~\ref{tab:2ljets_low}

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lcccccccc}
& $\metsig$
& $\mjj$
& $\mttwo$
& $\rll$
& $\dphillmet$
\\[1em]
SR-Low
& $6\textrm{--}9\textrm{--}12$
& $60\textrm{--}110$
& $> 80$
& $< 1$
&
\\[.5em]
\quad VR-Low
& $6\textrm{--}12$
& $60\textrm{--}110$
& $>80$
& $1\textrm{--}1.4$
&
\\[1em]
SR-Low-2
& $6\textrm{--}9$
& $60\textrm{--}110$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[.5em]
\quad VR-Low-2
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[1em]
CR-Z
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $> 80$
& $\uwave{\hphantom{< 1.6}}$
& $\uwave{\hphantom{< 0.6}}$
\end{tabular}
\small
\\[1em]
Common: Preselection,
$\njet = 2$,
$\nbtag = 0$,
$\mll \in 81\textrm{--}101\,\eV[G]$.
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS-EWK require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\GeV\ and $\met>100~\GeV$.
%Instead, VR-SS-EWK requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are \uwave{underlined}.
\TODO{caption}
}
\label{tab:2ljets_low}
\end{table}

@@

Table~\ref{tab:2ljets_offshell}

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lccccc}
& $\metsig$
& $\mll$
& $\mttwo$
& $\ptjone$
& $\dphijmet$
\\[1em]
SR-OffShell
& $>9$
& $12\textrm{--}40\textrm{--}71$
& $>100$
& $>100$
& $>2$
\\[.5em]
\quad VR-OffShell
& $>9$
&  12--71
& $\uwave{80\textrm{--}100}$
& $> 100$
& $> 2$
\\[1em]
CR-DY
& $\uwave{6\textrm{--}9}$
& $12\textrm{--}71$
& $> 100$
& $\uwave{\hphantom{> 100}}$
& $\uwave{\hphantom{> 2}}$
\end{tabular}
\small
\\[1em]
Common: Preselection,
$\njet \geq 2$,
$\nbtag = 0$.
\caption{%
Differences between regions are \uwave{underlined}.
\TODO{caption}
}
\label{tab:2ljets_offshell}
\end{table}

@@

\begin{itemize}
\item DR-High: SR-High-8
\item DR-$\ell\ell bb$: SR-$\ell\ell bb$
\item DR-Int: SR-Int
\item DR-Low: SR-Low
\item DR-OffShell: SR-OffShell
\end{itemize}
